---
title: "**About Myself**"
date: "Last Updated: Mar 19, 2022"
output: html_document
---

<style type="text/css">

h1.title {
  font-size: 38px;
  color: Black;
  text-align: center;
  font-size: 18pt;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  color: Black;
  text-align: center;
  font-size: 12pt;
}
</style>

Hello! This is Shibo. I am a recent graduate from Boston College with a Master of Science in applied economics. I am sincerely passionate about utilizing data analysis to uncover insights through statistical analysis and visualizations. I enjoy leveraging economic, demographic and sports data in making actionable and practical suggestions to inform decision making. Feel free to connect with me on LinkedIn! 



```{r include=FALSE}
batman_data <- data.frame(


  date_release = c("Master of Science in Applied Economics with GPA: 3.96/4.0
                    Graduate Certificate in Data Analytics",
                   "Bachelor of Science in Economics with GPA: 3.43/4.0
                    Economics Departmental Honors, Recipient of the Arthur J. Boynton Award and 
                    Dean’s list in 2019 & 2020"),

  title = c("Boston College",
                  "University of Kansas"),
  
  date_time = c("Aug 2020 - Dec 2021", 
                "Aug 2016 - July 2020"
  )
)
```

```{r, echo=FALSE}
library(cronologia)
create_tml_2(df = batman_data, # the data frame
           smr = "title", # the column that will be used in the summary 
           dsc = "date_time", # the column that will be used in the description
           dsc2 = "date_release", 
           smr_col = "black", 
           smr_bgcol = "#FFFFFF"
           )
```

